---
output: pdf_document
---
```{r, echo=FALSE, message=FALSE}
library(purrr)

source("scripts/summary_table/summary_fitting_once.R")
source("scripts/summary_table/summary_fitting_Btimes.R")
source("scripts/kable_graph/making_kable.R")
source("scripts/kable_graph/bias_graph.R")
```

# Testing different models (fitting one time)

## Using control only

### $\beta_0=-6$: prevalence $\approx0.01$

```{r, echo=FALSE, warning=FALSE}
sumamry_table <- fit_once(beta0 = -6, seed = 2025)$summary_table
make_reri_table(sumamry_table, beta0 = -6)
```

### $\beta_0=-5.5$: prevalence $\approx0.018$

```{r, echo=FALSE, warning=FALSE}
sumamry_table <- fit_once(beta0 = -5.5, seed = 2025)$summary_table
make_reri_table(sumamry_table, beta0 = -5.5)
```


\newpage


### $\beta_0=-5$: prevalence $\approx0.03$

```{r, echo=FALSE, warning=FALSE}
sumamry_table <- fit_once(beta0 = -5, seed = 2025)$summary_table
make_reri_table(sumamry_table, beta0 = -5)
```

### $\beta_0=-4.5$: prevalence $\approx0.05$

```{r, echo=FALSE, warning=FALSE}
sumamry_table <- fit_once(beta0 = -4.5, seed = 2025)$summary_table
make_reri_table(sumamry_table, beta0 = -4.5)
```


\newpage


### $\beta_0=-4$: prevalence $\approx0.08$

```{r, echo=FALSE, warning=FALSE}
sumamry_table <- fit_once(beta0 = -4, seed = 2025)$summary_table
make_reri_table(sumamry_table, beta0 = -4)
```

### $\beta_0=-3$: prevalence $\approx0.18$

```{r, echo=FALSE, warning=FALSE}
sumamry_table <- fit_once(beta0 = -3, seed = 2025)$summary_table
make_reri_table(sumamry_table, beta0 = -3)
```


\newpage


### $\beta_0=-2$: prevalence $\approx0.4$

```{r, echo=FALSE, warning=FALSE}
sumamry_table <- fit_once(beta0 = -2, seed = 2025)$summary_table
make_reri_table(sumamry_table, beta0 = -2)
```

### $\beta_0=-1$: prevalence $\approx0.6$

```{r, echo=FALSE, warning=FALSE}
sumamry_table <- fit_once(beta0 = -1, seed = 2025)$summary_table
make_reri_table(sumamry_table, beta0 = -1)
```


\newpage



## Using both control and case

### $\beta_0=-6$: prevalence $\approx0.01$

```{r, echo=FALSE, warning=FALSE}
sumamry_table <- fit_once(beta0 = -6, use = "both", seed = 2025)$summary_table
make_reri_table(sumamry_table, beta0 = -6)
```

### $\beta_0=-5.5$: prevalence $\approx0.018$

```{r, echo=FALSE, warning=FALSE}
sumamry_table <- fit_once(beta0 = -5.5, use = "both", seed = 2025)$summary_table
make_reri_table(sumamry_table, beta0 = -5.5)
```


\newpage


### $\beta_0=-5$: prevalence $\approx0.03$

```{r, echo=FALSE, warning=FALSE}
sumamry_table <- fit_once(beta0 = -5, use = "both", seed = 2025)$summary_table
make_reri_table(sumamry_table, beta0 = -5)
```

### $\beta_0=-4.5$: prevalence $\approx0.05$

```{r, echo=FALSE, warning=FALSE}
sumamry_table <- fit_once(beta0 = -4.5, use = "both", seed = 2025)$summary_table
make_reri_table(sumamry_table, beta0 = -4.5)
```


\newpage


### $\beta_0=-4$: prevalence $\approx0.08$

```{r, echo=FALSE, warning=FALSE}
sumamry_table <- fit_once(beta0 = -4, use = "both", seed = 2025)$summary_table
make_reri_table(sumamry_table, beta0 = -4)
```

### $\beta_0=-3$: prevalence $\approx0.18$

```{r, echo=FALSE, warning=FALSE}
sumamry_table <- fit_once(beta0 = -3, use = "both", seed = 2025)$summary_table
make_reri_table(sumamry_table, beta0 = -3)
```


\newpage


### $\beta_0=-2$: prevalence $\approx0.4$

```{r, echo=FALSE, warning=FALSE}
sumamry_table <- fit_once(beta0 = -2, use = "both", seed = 2025)$summary_table
make_reri_table(sumamry_table, beta0 = -2)
```

### $\beta_0=-1$: prevalence $\approx0.6$

```{r, echo=FALSE, warning=FALSE}
sumamry_table <- fit_once(beta0 = -1, use = "both", seed = 2025)$summary_table
make_reri_table(sumamry_table, beta0 = -1)
```